%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% cv-friggeri-x 1.0 (01/01/2016)
% XeLaTeX Template
%
% Based on:
% Friggeri Resume/CV
% Version 1.2 (3/5/15)
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
% 
% Modified by:
% Nadorrano
% https://github.com/Nadorrano/cv-friggeri-x
%
% License:
% MIT
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography,
% if used, needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,nocolors]{cv-friggeri-x}
% Add `a4paper` to set a4 paper size
% Add `nocolors` to remove colors from the document
% Add `lightheader` to change the dark background of the header to white

\usepackage{marvosym} % needed to print glyphs for email, cell phone etc.
\addbibresource{bibliography.bib} % Specify the bibliography file to include publications
\begin{document}

\header{Germán }{Gómez}{ iOS Developer } % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
~
\pin \hfill  Calle 82 #113-100
Bogotá, DC
Colombia
~
{\Large\textcolor{gray}{\Telefon}} \hfill +57 (1) 394 1756
{\Large\textcolor{gray}{\Mobilefone}} \hfill +57 (316) 802 1649
~
{ \href{mailto:ggomez1728@gmail.com}{ggomez1728@gmail.com}
~
\tlogo \hfill \href{http://twitter.com/gomez1728}{@ggomez1728}
\flogo \hfill \href{http://facebook.com/germanalbertogomezvargas}{fb://ggomez1728}
\llogo \hfill \href{http://linkedin.com/in/ggomez1728}{in://ggomez1728}
\vklogo \hfill \href{http://vk.com/id424921150}{vk://ggomez1728}
\gitlogo \hfill \href{http://github.com/ggomez1728}{git://ggomez1728}
~
\section{Programming}
\applelogo Swift, Objective-C, 
C++, PHP, Ruby,
{\color{red} $\varheartsuit$}  \LaTeX,  MATLAB,
JavaScript,
CSS3 \&  HTML5

\section{iOS Frameworks}
AVFoundation, CoreData, Social,
CoreMotion, CoreLocation, MapKit, 
UIKit, CoreBluetooth, SpriteKit \& WebKit

\section{Languages}
Spanish : Native language.
English: Intermediate (A2).


\section{Personal Interests}
\begin{itemize}
\item Play Go (Abstract strategy game).
\item Running.
\item Play Soccer.
\end{itemize}


\end{aside}
\\

\textbf{Currently:} M.Sc. Artificial Intelligence, iOS Developer at mvpLAB.

\textbf{Fields:} Project Management, Electronics and Software Development, Scrum

\textbf{Prefers:} Swift, Objective-C, C++, PHP, Assembly, Git

\\
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\subsection{Professional Experience}

\begin{entrylist}

\entry
{2016--Now}
{mvpLAB Ltd, Startup Accelerator Lab}
{London, United Kingdom}
{\emph{ iOS Developer} \\
Participant in the development of next native apps:
\begin{itemize}
\item Olitool app.
\item Ilocum app.
\item GAYDAR app (currently).
\end{itemize}}

%------------------------------------------------
\entry
{2015--2016}
{Araneus C.A.}
{Barquisimeto, Venezuela}
{\emph{Development Team Lead  \& Backend Developer - Pollinion App.}
\begin{itemize}
\item Chief Developer of the Pollinion App.
\item Developer Pollinion App using Swift language for iOS devices, with dependency manager
in COCOAPODS and use the Firebase for push-notifications.
\item Developer of the platform for Pollinion app based on a Restful services with PHP-Laravel
framework.
\item Manage Postgresql database administration assignments for diverse Apps Services.
\end{itemize}}

%------------------------------------------------

\entry
{2013--2015}
{Diodotec C.A.}
{Barquisimeto, Venezuela}
{\emph{Electronic Design Engineer \& Software Development}
\begin{itemize}
\item Automations process with PIC, Atmel, Arduino and Raspberry devices
\item Develops project with GSM-GPRS, RS-845, XBee and USART connections. Develop interface design with VB.net, PHP and mysql.
\end{itemize}}

%------------------------------------------------

\entry
{2011--2013}
{DSPElectronic C.A.}
{Barquisimeto, Venezuela}
{\emph{ Electronic Design Engineer } 
\begin{itemize}
\item Developing and implementing research and development procedures and techniques
for traffic lights
\item Hardware design and frameware development of traffic lights controllers, traffic lights
counters and develop remote connections (Green wave for series of traffic lights) by RS-
485 and wireless connection.
\end{itemize}}

%------------------------------------------------

\entry
{2011--2013}
{Consejo Legislativo del Estado Lara}
{Barquisimeto, Venezuela}
{\emph{Technical Support Specialist}
\begin{itemize}
\item Developer intranet Fondo Documental Lara.
\item Technical Support in Consejo Legislativo del Estado Lara.
\end{itemize}}

%------------------------------------------------
\end{entrylist}


\subsection{Academic Experience}

\begin{entrylist}

\entry
{2015}
{Univ. Fermín Toro}
{Barquisimeto, Venezuela}
{\emph{Speaker} \\
XIII Jornadas de Borrosidad y Sistemas Difusos, Topic: Fuzzy Logic Toolbox Vs Xfuzzy}

%------------------------------------------------

\end{entrylist}
\begin{entrylist}
\entry
{2012}
{Univ. Yacambú}
{Barquisimeto, Venezuela}
{\emph{Competitor} \\
Premio Eureka a la Innovatividad Universitaria, Work: Automating the process of in vitro propagation of horticultural plants, using a temporary immersion system}

%------------------------------------------------

\entry
{2009}
{Univ. Yacambú}
{Barquisimeto, Venezuela}
{\emph{Teaching assistant, UTA}
\begin{itemize}
\item Prepare and teach issues related to Systems Electronics Analog and Digital.
\item Prepare and teach issues related to Microcontroller Programming for Pic and Atmel.
\end{itemize}}
\end{entrylist}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}

%------------------------------------------------

\entry
{2014--2017}
{M.Sc. {\normalfont Artificial Intelligence}}
{Univ. Centroccidental Lisandro Alvarado}
{Master Thesis: Fuzzy logic algorithm for selecting projects for mobile applications using
vague criterias.\\
Relevant research activities:
\begin{itemize}
\item Developed of a Genetic Algorithm for six-hump camel function and others functions in C++.
\item Use of MobileRobots' Advanced Robot Interface for Applications (ARIA) in C++.
\item Data Mining with Open Source Machine Learning Software in Java (Weka 3).
\item Develop of fuzzy systems in MatLab and X-Fuzzy.
\end{itemize}
}

%------------------------------------------------

\entry
{2006--2010}
{Bachelor {\normalfont of Electronic and Computer}}
{Univ. Yacambú}
{Thesis: Automating the process of in vitro propagation of horticultural plants, using a
temporary immersion system\\
Design and Developed of the SCADA System for the in vitro laboratory.}

%------------------------------------------------

\end{entrylist}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Certifications}

\begin{entrylist}

%------------------------------------------------

\entry
{2016}
{iOS Development for Creative Entrepreneurs Specialization}
{University of California Irvine}
{This Specialization focuses on the basics of iOS application development, include uency
in Objective-C and UIKit and SpriteKit user interface concepts, and learn to leverage
networking, security, audio, video, location, and sensor frameworks}

%------------------------------------------------

\entry
{2016}
{iOS Development Specialization }
{Tecnológico de Monterrey}
{This Specialization focuses on the basics of iOS application development, include uency
in Swift and UIKit and SpriteKit user interface concepts, and learn to leverage networking,
security, audio, video, location, and sensor frameworks}

%------------------------------------------------

\entry
{2016}
{Ruby on Rails: An Introduction }
{Johns H. University}
{Explore how to build web applications with the Ruby on Rails web application framework,
which is geared towards rapid prototyping. Professionalized in research methods, software development and e-assessment}

%------------------------------------------------
\end{entrylist}
\\
\\
\\
\\
\\
\begin{flushright}
\textit{Working hard to keep things simple.}
\end{flushright}
\end{document}
